Binary companions of red giant stars in \apogee\ \DR

### 2018-03-01 paper/1-catalog/twoface-catalog.tex
With control sample

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{96,231}
\newcommand{\nvisits}{397,559}
\newcommand{\ncontrol}{16,384}
\newcommand{\nunimodal}{XX}
\newcommand{\nmultimodal}{XX}

@@

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even a very small number of observation epochs can be useful for detecting
companions, though such data can be difficult to use for characterizing
individual systems:
There can be multiple qualitatively different orbital solutions that fit the
data.
For these reasons, we custom-built a Monte Carlo sampler (\thejoker) that
delivers reliable (and often highly multi-modal) posterior samplings for
companion orbital parameters given sparse radial-velocity data.
% Aims
Here we perform a search for secondary companions of \nstars\ red-giant stars
observed in the \apogee\ survey (\DR) with $\geq 3$ spectroscopic epochs.
% Methods
We select stars with probable companions by making a cut on our posterior belief
about the amplitude of the stellar radial-velocity variation induced by the
orbit.
% Results
We provide (1)~a catalog of \nunimodal\ companions for which the stellar
companion properties can be confidently determined in a posterior sense, (2)~a
catalog of \nmultimodal\ stars that likely have companions, but for which
(in most cases) more observations would be needed to uniquely determine the
orbital properties, and (3)~posterior samplings for all orbital-companion
parameters for all stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}

@@

We select a sample of stars that confidently have companions using percentiles
computed from the posterior samples in the velocity semi-amplitude parameter,
$K$.
\figurename~\ref{fig:lnK-percentiles}, left panel, shows distributions of
percentiles in $\ln K$ computed for all stars with posterior samplings from
\thejoker.
\figurename~\ref{fig:lnK-percentiles}, right panel, shows the same for posterior
samplings for the null control sample.
We define a cut in the \todo{XX} percentile of the $\ln K$ samples such that
\todo{XX false-positives...} (vertical line in
\figurename~\ref{fig:lnK-percentiles}); \nmultimodal\ stars pass this cut.

% % Notebook: "TODO"
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\textwidth]{lnK-percentiles}
% \end{center}
% \caption{%
% TODO
% \label{fig:lnK-percentiles}
% }
% \end{figure}

>>>>

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{96,231}
\newcommand{\nvisits}{397,559}
\newcommand{\ncontrol}{16,384}
\newcommand{\nhighK}{4,510}
\newcommand{\nunimodal}{XX}
\newcommand{\nmultimodal}{XX}

@@

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even a very small number of observation epochs can be useful for detecting
companions, though such data can be difficult to use for characterizing
individual systems:
There can be multiple qualitatively different orbital solutions that fit the
data.
For these reasons, we custom-built a Monte Carlo sampler (\thejoker) that
delivers reliable (and often highly multi-modal) posterior samplings for
companion orbital parameters given sparse radial-velocity data.
% Aims
Here we perform a search for secondary companions of \nstars\ red-giant stars
observed in the \apogee\ survey (\DR) with $\geq 3$ spectroscopic epochs.
% Methods
We select stars with probable companions by making a cut on our posterior belief
about the amplitude of the stellar radial-velocity variation induced by the
orbit.
% Results
We provide (1)~a catalog of \nunimodal\ companions for which the stellar
companion properties can be confidently determined in a posterior sense, (2)~a
catalog of \nhighK\ stars that likely have companions, but for which
(in most cases) more observations would be needed to uniquely determine the
orbital properties, and (3)~posterior samplings for all orbital-companion
parameters for all stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}

@@

We select a sample of stars that confidently have companions using percentiles
computed from the posterior samples in the velocity semi-amplitude parameter,
$K$.
\figurename~\ref{fig:lnK-percentiles}, shows the distribution of 1st percentiles
of $\ln K$ computed for all stars with posterior samplings from \thejoker\
(filled, blue histogram), along with the same for posterior samplings for the
null control sample (solid line, black).
To select stars with companions, we use a cut in the 1st percentile of the $\ln
K$ samples such that $<1\%$ of the control sample is selected, i.e. our
estimated false positive rate is $<1\%$.
We use a threshold of $\ln K = 0$ to meet this constraint (vertical, dashed line
in \figurename~\ref{fig:lnK-percentiles}); \nhighK\ stars pass this cut.

% Notebook: "Sample K cuts.ipynb"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{lnK-percentiles}
\end{center}
\caption{%
TODO
\label{fig:lnK-percentiles}
}
\end{figure}
